Providing better confidentiality and authentication on the Internet using Namecoin and MinimaLT

### 2014-01-10 paper.tex
Fix a few typos and a couple sentences.

Zooko's triangle says that out of these three properties \cite{zookoTriangleWikipedia}, a naming system can only have two.
\begin{itemize}
\item \emph{Secure}\footnote{We can't agree with the naming of this property given the threat model we described previously in this paper.}: The quality that there is one, unique and specific entity to which the name maps.
\item \emph{Global}: The lack of a centralized authority for determining the meaning of a name. Instead, measures such as a Web of trust are used.
\item \emph{Memorable}: The quality of meaningfulness and memorability to the users of the naming system.
\end{itemize}

@@

Private-public key pairs are generated\footnote{The curved used in Bitcoin is \emph{secp256k1} which is surprisingly a NIST recommended curve.} when creating a new Bitcoin addresses.

@@

A few months ago, a previously unknown email provider called \emph{Lavabit} was under pressure from the US government to hand over its private SSL key. The reason turned out to be that Edward Snowden was using the email service. If Lavabit had turned over the SSL keys, they would have compromised the privacy of their entire user base. This is due to poorly configured SSL where the ECDHE is not the default. ECDHE performs a Elliptic curve Diffie–Hellman key exchange. The last E from ECDHE stands for Ephemeral which means that a new key, that will never be stored, is generated at every handshake. Hence, even if the server gets compromised or the network operator is forced to hand over an encryption key, he won't be able to provide it. Unfortunately, most system administrators don't put the \emph{ECDHE} ciphers on top of their ciphers list resulting in the lack of Perfect Forward Secrecy.

@@

Thanks to the structure of MinimaLT packets, the \emph{tunnel ID} is what identifies what packet belongs to what connection and therefore, MinimaLT has complete IP mobility. Unlike TCP, the source IP address and UDP port can change without affecting the connection. A specific RPC (\emph{$\text{nextTid}_{0}$}) exists to announce an IP address change. A change in IP address will cause a rekeying, a procedure that we describe a little further. The fact that we have IP mobility is a big advantage over TCP that currently struggles in the mobile world when switching from a WiFi connection to a 3G/4G signal for instance. MinimaLT solves by design many problems that plague TCP today such as multi-path TCP!

>>>>

Zooko's triangle says that out of these three properties \cite{zookoTriangleWikipedia}, a naming system can only have two.
\begin{itemize}
\item \emph{Secure}\footnote{We cannot agree with the naming of this property given the threat model we described previously in this paper.}: The quality that there is one, unique and specific entity to which the name maps.
\item \emph{Global}: The lack of a centralized authority for determining the meaning of a name. Instead, measures such as a Web of trust are used.
\item \emph{Memorable}: The quality of meaningfulness and memorability to the users of the naming system.
\end{itemize}

@@

Private-public key pairs are generated\footnote{The curve used in Bitcoin is \emph{secp256k1} which is surprisingly a NIST recommended curve.} when creating a new Bitcoin addresses.

@@

A few months ago, a previously unknown email provider called \emph{Lavabit} was under pressure from the US government to hand over its private SSL key. The reason turned out to be that Edward Snowden was using the email service. If Lavabit had turned over the SSL keys, they would have compromised the privacy of their entire user base. This is due to poorly configured SSL where the ECDHE is not the default. ECDHE performs an Elliptic curve Diffie-Hellman key exchange. The last E from ECDHE stands for Ephemeral which means that a new key, that will never be stored, is generated at every handshake. Hence, even if the server gets compromised or the network operator is forced to hand over an encryption key, he won't be able to provide it. Unfortunately, most system administrators don't put the \emph{ECDHE} ciphers on top of their ciphers list resulting in the lack of Perfect Forward Secrecy.

@@

Thanks to the structure of MinimaLT packets, the \emph{tunnel ID} is what identifies what packet belongs to what connection and therefore, MinimaLT has complete IP mobility. Unlike TCP, the source IP address and UDP port can change without affecting the connection. A specific RPC (\emph{$\text{nextTid}_{0}$}) exists to announce an IP address change. A change in IP address will cause a rekeying, a procedure that we describe further down. The fact that we have IP mobility is a big advantage over TCP that currently struggles in the mobile world when switching from a WiFi connection to a 3G/4G signal for instance. MinimaLT solves by design many problems that plague TCP today such as multi-path TCP!
